Sbert

### 2022-06-14 code/text_analysis.Rmd
try add graphs

game_convergence <- M_mat %>% 
  group_by(gameId,game_cond) %>% 
  mutate(combinedId=str_c(playerId,repNum,sep="_")) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, into=c("playerId_1","repNum_1"), convert=T, sep="_") %>% 
  separate(dim2, into=c("playerId_2","repNum_2"), convert=T, sep="_") %>% 
  mutate(repDist=abs(repNum_1-repNum_2),
         earlierRep=ifelse(repNum_1>repNum_2,repNum_2,repNum_1),
         samePlayer=ifelse(playerId_1==playerId_2,1,0)) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  ungroup()

m_convergence <- lmer(sim ~ repDist*game_cond+samePlayer+earlierRep*game_cond + (1|gameId), data=game_convergence)

@@

game_divergence <- M_mat %>% 
  group_by(game_cond) %>% 
  mutate(combinedId=str_c(gameId,repNum,sep="_")) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, into=c("gameId_1","repNum_1"), convert=T, sep="_") %>% 
  separate(dim2, into=c("gameId_2","repNum_2"), convert=T, sep="_") %>% 
  filter(gameId_1!=gameId_2) %>% 
  mutate(repDist=abs(repNum_1-repNum_2),
         earlierRep=ifelse(repNum_1>repNum_2,repNum_2,repNum_1)) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  ungroup()

>>>>

game_convergence <- M_mat %>% 
  group_by(gameId,game_cond) %>% 
  mutate(combinedId=str_c(playerId,repNum,sep="_")) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, into=c("playerId_1","repNum_1"), convert=T, sep="_") %>% 
  separate(dim2, into=c("playerId_2","repNum_2"), convert=T, sep="_") %>% 
  mutate(repDist=abs(repNum_1-repNum_2),
         earlierRep=ifelse(repNum_1>repNum_2,repNum_2,repNum_1),
         samePlayer=ifelse(playerId_1==playerId_2,1,0)) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  filter(!is.na(samePlayer)) %>% 
  ungroup()

0 is not same speaker, 1 is same speaker.

```{r}
game_convergence %>% filter(repDist<5) %>% ggplot(aes(x=earlierRep, y=sim, color=repDist))+geom_point(alpha=.1)+geom_smooth()+facet_grid(game_cond~samePlayer)+labs(title="Rep distance <5")

game_convergence %>% ggplot(aes(x=repDist, y=sim, color=earlierRep))+geom_point(alpha=.01)+geom_smooth()+facet_grid(game_cond~samePlayer)

We're not really seeing much, similarity is higher in rounds that are closer together, but if we only look at relatively close reps (within 5 of each other), there's not much by way of pattern.

```{r, eval=F}
m_convergence <- lmer(sim ~ repDist*game_cond+samePlayer+earlierRep*game_cond + (1|gameId), data=game_convergence)

@@

game_divergence <- M_mat %>% 
  group_by(game_cond) %>% 
  mutate(combinedId=str_c(gameId,repNum,sep="_")) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, into=c("gameId_1","repNum_1"), convert=T, sep="_") %>% 
  separate(dim2, into=c("gameId_2","repNum_2"), convert=T, sep="_") %>% 
  filter(gameId_1!=gameId_2) %>% 
  mutate(repDist=abs(repNum_1-repNum_2),
         earlierRep=ifelse(repNum_1>repNum_2,repNum_2,repNum_1)) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  ungroup()
```

```{r}
game_divergence %>% filter(repDist==0) %>% ggplot(aes(x=earlierRep, y=sim))+geom_point(alpha=.1)+geom_smooth()+facet_grid(game_cond~.)+labs(title="Rep distance == 0")

game_divergence %>% ggplot(aes(x=repDist, y=sim, color=earlierRep))+geom_point(alpha=.01)+geom_smooth()+facet_grid(game_cond~.)

Not seeing anything useful here.

```{r, eval=F}
